---
title: "Example1"
author: "Jacob Miller"
date: "February 13, 2019"
output: 
  html_document:
    theme: spacelab
    toc: true
    number_sections: true
---

Your instructions:
Turn Motor Trend Car Road Tests into a first level header
Turn the word description into a second level header.
Put the word fuel in monospaced font (for code).
Italicize the words 1974 Motor Trend US magazine.
Link the work Biometrics to www.google.com.
Create an ordered list of the steps to take.
Create a bulleted list of the afterparty celebrations.
For future reference, include a Latex formula. Put two dollar signs around kelvin = celsius - 273.15.
That way we can remind ourselves how cold it will be when the universe turns dark.
Put in a line informing us of the date with single backticks today's date. Use r Sys.Date().
Go to the coding section below for further instructions.


# Motor Trend Car Road Tests

## Description

The data was extracted from the *1974 Motor Trend US magazine*, and comprises `fuel` consumption and 10 aspects of automobile design and performance for 32 automobiles (1973-74 models).

Source

Henderson and Velleman (1981), Building multiple regression models interactively. [Biometrics](google.com), 37, 391-411.

Steps to take

1. Perform exploratory data analysis
2. Evaluate correlations
3. Run a linear regression

Afterparty celebrations

* Non-caffeinated Barq's root beer
* Proper rest

$$ kelvin = celcius - 273.15 $$


Today's date is `r Sys.Date()`

Let's start coding--
Create a code block showing the first 5 lines of the mtcars dataset.
```{r First Five Lines}
head(mtcars)
```

Create a scatterplot with mpg on the x axis and cyl on the y axis.
```{r Scatterplot1}
plot(mtcars$mpg, mtcars$cyl)
```

Load the dplyr library, but suppress the messages associated with it.
```{r dplyr is the name of the library,  message = FALSE, warning = FALSE}
library(dplyr)

```

Run three separate chunks of code with some basic manipulations of the mtcars dataset, but with different chunk options. Run echo=FALSE, eval=FALSE, and results='hide'. What is the difference between them?
```{r manipulation1, echo = FALSE}
  example1 <- mean(mtcars$mpg)
  example1
```

```{r manipulations2, eval = FALSE}
  example2 <- mean(mtcars$mpg)
  example2
```

```{r manipulations3, results = 'hide'}
  example3 <- mean(mtcars$mpg)
  example3
```

Create a graph and use fig.height = 4 and fig.width = 5 as chunk options. What do you notice?
```{r}
plot(mtcars$cyl, mtcars$mpg)
```

Use output: html_document: theme:spacelab with proper indentation to check out what can be done visually. Add toc: true as well to check out the automatic table of contents.
