---
title: "FinalProject"
author: "Andrew Clemons"
date: "4/20/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Solution
Here is the code for what I finding the amount of wasted ad spending. I first created a 56 day lead that we used to predict what product would run out of stock and then calculated how much money was wasted on advertising. I then calculated the amount of money that was wasted the week prior because that money was probably not used to its fullest if we ran out of product. The last chunk is just the aggregation of what you were asking for. I calculated the lags for the whole week, and hope the implementation was what you were thinking. I also spent time working on jeffs approach even though what he was pulling was different. 

# Code

```{r code, eval=FALSE}
library(imputeTS)
library(forecast)
library(tidyverse)
library(lubridate)
library(zoo)

df <- readr::read_csv("training_data_20200403.csv")
names(df)
df$avg_retail_price <- df$sales / df$units
df[is.nan(df$avg_retail_price),"avg_retail_price"] <- NA
df$multiple_vendors <- (df$vendor_id_max == df$vendor_id_min)
df$asin <- as.factor(df$asin)
df$ordering_region <- as.factor(df$ordering_region)
df$basket_size <- df$units / df$order_items_total
df[is.nan(df$basket_size),"basket_size"] <- 0

#### Chunk 1 Wasted Ad spend ####
# To-do --
# 1) Calculate adspend on products on date (like below)
# except omit the dates preceding periods where the product
# is never purchased again (0 for available
# going forward, or available for at least eight weeks going forward)
# If they are advertising a product they are intentionally stocking out
# of because it's seasonal or they don't want to carry it anymore,
# that's okay
temp <- df
ad <- temp %>%
  filter(available <= 0, ad_spend > 0) %>% #product isn't purchased again
  arrange(asin, ordering_region) %>%
  group_by(asin, ordering_region) %>%
  mutate(lead56 = lead(units, 56)) %>% #available for next 8 weeks
  filter(lead56 > 0 ) %>% #products are potentially ordered
  summarise(ad_waste = sum(ad_spend))

sum(ad$ad_waste)

# 2) How much is the ad spending in the preceding week (not just final date)
# before stockout? Apply the cleaning step from #1.

previous <- temp %>%
  filter(available <= 0, ad_spend > 0) %>%
  arrange(asin,ordering_region) %>%
  group_by(asin,ordering_region) %>%
  mutate(lag1 = lag(ad_spend, 1), 
         lag2 = lag(ad_spend, 2),
         lag3 = lag(ad_spend, 3),
         lag4 = lag(ad_spend, 4),
         lag5 = lag(ad_spend, 5),
         lag6 = lag(ad_spend, 6),
         lag7 = lag(ad_spend, 7)) %>%
  summarise(PreviousWeek = sum(lag7 + lag6 + lag5 + lag4 + lag3 + lag2+ lag1, na.rm = TRUE))

sum(previous$PreviousWeek)

# 3) Aggregate #2 this spending by ordering_region, asin, and month (floor_date(x,unit = "month"))
# Have a Unproductive AdSpend, Units, Total Revenue, Average Price, and Average Wholesaleprice
# in this summary table. Only include Jan-01-2019 going forward.

table <- temp %>%
  filter(available <= 0, ad_spend > 0) %>%
  group_by(ordering_region, asin, YMD = floor_date(date, unit = "month")) %>%
  mutate(lag1 = lag(ad_spend, 1), 
         lag2 = lag(ad_spend, 2),
         lag3 = lag(ad_spend, 3),
         lag4 = lag(ad_spend, 4),
         lag5 = lag(ad_spend, 5),
         lag6 = lag(ad_spend, 6),
         lag7 = lag(ad_spend, 7)) %>%
  mutate(WastedAdSpending = lag7 + lag6 + lag5 + lag4 + lag3 + lag2 + lag1, Revenue = sales)

table <- table %>%
  select(ordering_region, asin, YMD, WastedAdSpending, units, Revenue, avg_retail_price, max_wholesale_price)

  
summary(table)


```