---
title: "Milestone 2"
author: "Andrew Clemons"
date: "4/14/2020"
output:
  html_document: default
  pdf_document: default
---

# ARMA and ARIMA
Micah and I split up what we were assigned, he would tackle the value of advertising and I would look at creating the ARMA and ARIMA models. I played around with time series models, converting data frames to a ts object and univariate data sets. This is where I ran into a lot of confusion and I didn't come up with an answer. The temp data we have isn't a time series object and I could figure out how to convert it without lossing significant amounts of data.

I don't know how to move the data to the proper format and input that into a model based on groups. I found a few articles on how to do it using the broom and tidy packages, but when I tried to run them they would error and Google didn't have any answers. 

This is how I attempted to go about the problem, but it errors
```{r group, eval=FALSE}
group <- temp %>%
  group_by(asin, ordering_region) %>%
  do(ts <- arime(temp$lag_7_units))
  
```

I ended up with this, which they all have similar results
```{r single, eval = FALSE}
a1 <- arima(temp$lag_1_units)
a2 <- arima(temp$lag_2_units)
a3 <- arima(temp$lag_3_units)
a4 <- arima(temp$lag_4_units)
a5 <- arima(temp$lag_5_units)
a6 <- arima(temp$lag_6_units)
a7 <- arima(temp$lag_7_units)
```

Where did I go wrong, what was I supposed to do and how would you go about this because I've spent as much time as I could on this and all I got is a big headache. 